---
title: "Boot Test"
author: Odalys Barrientos
output: html_notebook
---

```{r, message=FALSE}
library(readr)

UserIDs <- read_csv("Username-IDs/UserIDs.csv")
viral.users <- which(UserIDs$category == "Viral")

InfoM <- read_csv("transCSSR-master/InfoMeasuresData.csv")
InfoM$category <- UserIDs$category
InfoM <- InfoM[which(InfoM$category == "Famous" | InfoM$category == "ForYou" ),]

LL <- read_csv("transCSSR-master/LogLossDat.csv")
LL$category <- UserIDs$category
LL$Difference <- LL$LLGAM-LL$LLCSSR
# Positive = CSSR is better
# Negative = GAM is better 
LL <- LL[which(LL$category == "Famous" | LL$category == "ForYou" ),]
```
# Boot Median function
```{r}
diff.medians <- function(x, i){
    xboot <- x[i,]
    group1.inds <- xboot$group == 1 
    famous.scores <- xboot[group1.inds,1]
    group2.inds <- xboot$group == 2
    foryou.scores <- xboot[group2.inds,1]

    d.med <- median(famous.scores)-median(foryou.scores)
    return(d.med)
}
```

# LL Differences : t test
```{r, message = FALSE}
library(MKinfer)
library(mosaic)
library(boot)

boot.t.test(Difference ~ category, data=LL)
```
bootstrapped p-value = 0.5943 
95 percent bootstrap percentile confidence interval:
 -0.008311303  0.014436826
sample estimates:
mean in group Famous | mean in group ForYou 
          0.01677871 |   0.01267528 

Mean for difference in log loss in both groups are positive thus both famous and foryou groups prefer the CSSR model. 


# LLGAM: Median
```{r}
scoresbygroup <- data.frame(score = LL$LLGAM, group = ifelse(LL$category=="Famous",1, 2))
scoresbygroup <- scoresbygroup[!is.na(scoresbygroup$score),]


b <- boot(data = scoresbygroup, statistic = diff.medians, R=2000, strata = scoresbygroup$group)

boot.ci(b, type = 'bca')

diff.medians(scoresbygroup, i = 1:nrow(scoresbygroup))

aggregate(score ~ group, data = scoresbygroup, FUN = median)$score
```
# LLGAM: Mean
```{r}

boot.t.test(LLGAM ~ category, data=LL)
```
bootstrapped p-value = 0.1328 
95 percent bootstrap percentile confidence interval:
 -0.006077797  0.049560263
sample estimates: 
mean in group Famous | mean in group ForYou 
    0.08775446       |    0.06642447 

Mean in group Famous is slightly higher (by 0.021). In this sample, the famous group has a higher log loss as opposed to the ForYou group. We do not have statistically significant pvalue, thus there is not enough evidence that there is a true difference between the log loss for the GAM model for the famous vs ForYou group. 

# LLCSSR: Median
```{r}
scoresbygroup <- data.frame(score = LL$LLCSSR, group = ifelse(LL$category=="Famous",1, 2))
scoresbygroup <- scoresbygroup[!is.na(scoresbygroup$score),]


b <- boot(data = scoresbygroup, statistic = diff.medians, R=2000, strata = scoresbygroup$group)

boot.ci(b, type = 'bca')

diff.medians(scoresbygroup, i = 1:nrow(scoresbygroup))

aggregate(score ~ group, data = scoresbygroup, FUN = median)$score
```

# LLCSSR
```{r}
boot.t.test(LLCSSR ~ category, data=LL)
```
bootstrapped p-value = 0.1064 
95 percent bootstrap percentile confidence interval:
 -0.003564687  0.039631635
sample estimates:
mean in group Famous | mean in group ForYou 
          0.07097575 |      0.05374919 
          
Mean in group Famous is slightly higher (by 0.017)(could this inidcate the famous group is a harder group to predict???). 
In this sample, the famous group has a higher log loss as opposed to the ForYou group. We do not have statistically significant pvalue, thus there is not enough evidence that there is a true difference between the log loss for the CSSR model for the famous vs ForYou groups. 

# Hmu: Median
```{r}
scoresbygroup <- data.frame(score = InfoM$Hmu, group = ifelse(InfoM$category=="Famous",1, 2))
scoresbygroup <- scoresbygroup[!is.na(scoresbygroup$score),]


b <- boot(data = scoresbygroup, statistic = diff.medians, R=2000, strata = scoresbygroup$group)

boot.ci(b, type = 'bca')

diff.medians(scoresbygroup, i = 1:nrow(scoresbygroup))

aggregate(score ~ group, data = scoresbygroup, FUN = median)$score
```

#Hmu : Entroy Rate (Randomness (1 = random))
```{r}
boot.t.test(Hmu ~ category, data = InfoM)
```
bootstrapped p-value = 0.5461 
95 percent bootstrap percentile confidence interval:
 -0.02135636  0.04021306
sample estimates:
mean in group Famous  | mean in group ForYou 
          0.09467219  |     0.08538331 
          
Mean in group Famous is slightly higher (by 0.009)
(the difference is basically nothing but in this sample famous users have a slighly higher entropy rate so their behavior is slightly more random than ForYou users) 

In this sample, the famous group has a higher entropy rate as opposed to the ForYou group. We do not have statistically significant pvalue, thus there is not enough evidence that there is a true difference between the entropy rate for the famous vs ForYou groups.

# E: Median
```{r}
scoresbygroup <- data.frame(score = InfoM$E, group = ifelse(InfoM$category=="Famous",1, 2))
scoresbygroup <- scoresbygroup[!is.na(scoresbygroup$score),]


b <- boot(data = scoresbygroup, statistic = diff.medians, R=2000, strata = scoresbygroup$group)

boot.ci(b, type = 'bca')

diff.medians(scoresbygroup, i = 1:nrow(scoresbygroup))

aggregate(score ~ group, data = scoresbygroup, FUN = median)$score
```

# E: Memory
```{r}
boot.t.test(E ~ category, data = InfoM)
```
bootstrapped p-value = 0.7361 
95 percent bootstrap percentile confidence interval:
 -0.3706005  0.5630562
sample estimates:
mean in group Famous | mean in group ForYou 
           0.2722178 |    0.1942425 

(the difference is basically is very small but famous users tend to need more memory than forYou users)
In this sample, the famous group has a higher E as opposed to the ForYou group. We do not have statistically significant pvalue, thus there is not enough evidence that there is a true difference between E for the famous vs ForYou groups. 

# Cmu: Median
```{r}
scoresbygroup <- data.frame(score = InfoM$Cmu, group = ifelse(InfoM$category=="Famous",1, 2))
scoresbygroup <- scoresbygroup[!is.na(scoresbygroup$score),]


b <- boot(data = scoresbygroup, statistic = diff.medians, R=2000, strata = scoresbygroup$group)

boot.ci(b, type = 'bca')

diff.medians(scoresbygroup, i = 1:nrow(scoresbygroup))

aggregate(score ~ group, data = scoresbygroup, FUN = median)$score
```

# Cmu: 
```{r}
boot.t.test(Cmu ~ category, data = InfoM)
```
bootstrapped p-value = 0.3852 
95 percent bootstrap percentile confidence interval:
 -0.2930788  0.1032197
sample estimates:
mean in group Famous | mean in group ForYou 
           0.2380611 |   0.3204938 
           
Mean in group ForYou is slightly higher (by 0.082)
The difference is small but in this sample of users we can see that the users in the ForYou group have slightly more complaicated models than famous users. 

In this sample, the foryou group has a higher Cmu as opposed to the famous group. We do not have statistically significant pvalue, thus there is not enough evidence that there is a true difference between the entropy rate for the famous vs ForYou groups. 


# Overall

There are no statistically significant differences between the famous group and foryou group when looking at log loss (tells us which model fits best) and looking and the information measures (from CSSR). 

From sample means we can see that in our sample famous users have more random behavior and less complicated models where foryou users have less random behavior and more complicated models. 
Also famous groups have to use more "memory" (E) than foryou users in order to model the users behavior. 

