---
title: "Demo Choosing Smoothing Parameter for `gam()` Using Cross-validation"
author: "David Darmon"
date: "21 September 2021"
---

# Set Up Parallel Cluster for Faster Computation

```{r, message = FALSE}
# install.packages('doParallel')

library(doParallel)
cl <- makeCluster(8)
registerDoParallel(cl)
```

# Load in One User's Data to Demonstrate

```{r}
which.user <- 63

# Read in by-week data as data.frame.

dat <- read.table(sprintf('BinSeq-MatrixWSpaces/matrix-%g.txt', which.user), sep = ' ', header = FALSE)

# Convert to matrix

dat <- data.matrix(dat)

# Take transpose to make column-oriented (one week per column), so 
# can flatten easily into long vector.

Y <- t(dat)

# Flatten matrix to long vector.

dim(Y) <- NULL

# Get out design points as clock times.

x <- rep(1:ncol(dat), nrow(dat))
```

# Show Activity Over Time and Within Weeks

```{r}
par(mfrow = c(1, 2))

plot(Y, pch = 16, cex = 0.1)
plot(x, Y, pch = 16, cex = 0.1)
```

# Select Smoothing Parameter Using Cross-validation

```{r}
library(gam)
```

```{r}
source('cv-clock-gam.R')

cv.out <- cv.clock.gam(dat)
```

# Show Cross-validated Negative Log-likelihood as a Function of the Smoothing Parameter

```{r, warning = FALSE}
plot(cv.out$spars, cv.out$negative.LLs, 
     xlab = 'Smoothing Parameter',
     ylab = 'CV-ed Negative Log-Likelihood')
abline(v = cv.out$spar.star)
```

# Fit the GAM at the Optimal Smoothing Parameter

```{r, warning = FALSE}
mod.unpadded <- gam(Y ~ s(x, spar = cv.out$spar.star), family = binomial)

plot(predict(mod.unpadded, type = 'response')[1:ncol(dat)], type = 'l', ylim = c(0, 0.2),
     xlab = 'Time (1/2 Hour Segments)', ylab = 'Probability User is Active')
points(x, Y*0.2, pch = 16, cex = 0.1)

# Add smoothing spline fit via least-squares for comparison
lines(smooth.spline(x, Y), col = 'red', lty = 2)
```

# Demo Left- and Right-Padding

## Pad the data

```{r}
# dat <- matrix(rep(1:(336*5)), nrow = 5, ncol = 336, byrow = TRUE) # Test case checking the padding

prepost.pad.amount <- 48

dat.padded <- cbind(matrix(0, nrow = nrow(dat), ncol = prepost.pad.amount),
                    dat,
                    matrix(0, nrow = nrow(dat), ncol = prepost.pad.amount))

dat.padded[2:nrow(dat.padded), 1:(prepost.pad.amount)] <- 
  dat[1:(nrow(dat)-1), (ncol(dat) - prepost.pad.amount + 1):ncol(dat)]

dat.padded[1:(nrow(dat.padded)-1), (ncol(dat.padded)-prepost.pad.amount + 1):ncol(dat.padded)] <-
  dat[2:(nrow(dat.padded)), 1:prepost.pad.amount]

# Drop first and last week, since 0-padded:

dat.padded <- dat.padded[2:(nrow(dat.padded) - 1), ]

Y.padded <- t(dat.padded)

dim(Y.padded) <- NULL
```

## Fit the Model and Plot

```{r}
cv.out <- cv.clock.gam(dat.padded)
```

```{r}
x.wrapped <- rep(cv.out$clock.ticks, nrow(dat.padded))

mod.padded <- gam(Y.padded ~ s(x.wrapped, spar = cv.out$spar.star), family = binomial)

plot(predict(mod.padded, type = 'response')[(1+prepost.pad.amount):(ncol(dat.padded) - prepost.pad.amount)], type = 'l', ylim = c(0, 0.2),
     xlab = 'Time (1/2 Hour Segments)', ylab = 'Probability User is Active')
points(x.wrapped, Y.padded*0.2, pch = 16, cex = 0.1)
```

## Compare Unpadded and Padded Fits

```{r}
fit.without.padding <- predict(mod.unpadded, type = 'response')[1:ncol(dat)]

fit.with.padding <- predict(mod.padded, type = 'response')[(1+prepost.pad.amount):(ncol(dat.padded) - prepost.pad.amount)]
```

```{r}
plot(fit.without.padding, type = 'l', col = 'red',
     xlab = 'Time (1/2 Hour Segments)', ylab = 'Probability User is Active',
     ylim = c(0, 0.2))
lines(fit.with.padding, type = 'l', col = 'blue')
legend('topright', legend = c('Unwrapped', 'Wrapped'), col = c('red', 'blue'), lty = 1)
```

